Algebraic Principles for Concurrency Verification Tools

### 2013-10-04 Paper/paper.tex
Added some KA background and abstract sentence

\begin{abstract}
\end{abstract}

@@

>>>>

\begin{abstract}
We investigate the laws required for the derivation of the
rely/guarantee and owicki-gries inference rules in a minimalistic
algebraic setting based on Kleene algebra...
\end{abstract}

@@

A \emph{dioid} or \emph{idempotent semiring} is an structure
$(D,+,\cdot,0,1)$ such that $(D,+,0)$ is a join semilattice with zero,
$(D,\cdot,1)$ is a monoid, $+$ distributes over $\cdot$ from both the
right and left, and $0$ is a right and left annihilator for
$\cdot$. The natural partial order $\le$ is defined as $x \le y $ iff
$x + y = y$.

A Kleene algebra extends a dioid with a star operation satisfying the
following laws.
\begin{align*}
  1 + xx^* &\le x^* &\qquad z + xy \le y &\implies x^*z \le y\\
  1 + x^*x &\le x^* &\qquad z + yx \le y &\implies zx^* \le y
\end{align*}

In the context of programs, one typically thinks of $\cdot$ as being
sequential composition, $+$ as non-deterministic choice, $0$ as the
abortive action, $1$ as skip and $1$ as finite iteration. For
concurrent software, it is natural to extend the notion of a dioid to
that of a \emph{trioid} with operators for both sequential and
parallel composition. One can also axiomatise a parallel star
operation, but this seems to be a less useful operation. A
dioid or trioid is \emph{weak} if it does not satisfy $x0 = 0$.

Formally, a trioid is a structure $(D,+,\cdot,\|,0,1)$, such that
both $(D,+,\cdot,0,1)$ and $(D,+,\|,0,1)$ are dioids. Previous work in
this area has focused on identifying laws linking the sequential and
parallel composition operators, notably, the exchange law
\begin{align*}
  (a \| b) \cdot (c \| d) \le (a \cdot d) \| (b \cdot c).
\end{align*}
The exchange law is appealing as it provides a way to derive many
properties of parallel composition from a single law. For example, one
can show that $\|$ must be commutative, that $x \cdot y \le x \| y$
